Security performance in the Android ecosystem

### 2015-06-03 security_scoring.tex
Add TODO
Discuss the uncertainty calculation for m (badly)

We can compute the uncertainty for $f$ and $u$.
$f$ is calculated by taking the total secure device days and dividing it by the total insecure and secure device days.
The total secure device days and total insecure device days are both counting experiments and so their measurement error is their square root~\cite{Taylor1997}.
Since the numbers involved are large, the uncertainty in $f$ is small.
$u$ is computed by taking the sum of the proportions of devices running the most recent version each day, both the count of devices running the maximum version and total count have square root uncertainties.
The Python \texttt{uncertainties} library was used to propagate uncertainties through calculations.

@@

\subsubsection{Sensitivity of scoring metric}
\daTabDLDistances
\daTabChangeInScores
To evaluate whether the ranking of different manufacturers is sensitive to the form of the scoring metric we computed the normalised Damerau-Levenshtein distance~\cite{Bard2007} between the lists ordered using different forms of the scoring metric, this is shown in Table~\ref{tab:dl_distances}.
The `equal' metric weights $f$, $u$ and $m$ equally rather than favouring $f$ and makes little difference.
Changing the scoring metric also impacts the scores given for each entity Table~\ref{tab:change_in_scores} shows the mean impact on the scores.

>>>>

We can compute the uncertainty for $f$, $u$ and $m$.
$f$ is calculated by taking the total secure device days and dividing it by the total insecure and secure device days.
The total secure device days and total insecure device days are both counting experiments and so their measurement error is their square root~\cite{Taylor1997}.
Since the numbers involved are large, the uncertainty in $f$ is small.
$u$ is computed by taking the sum of the proportions of devices running the most recent version each day, both the count of devices running the maximum version and total count have square root uncertainties.
$m$ is computed by counting the number of vulnerabilities which affected that entity and which have not yet been fixed on any device we have observed from that entity.
However it could be that the entity has released a fix to some devices but we have not yet observed a device with that fix and so the uncertainty in each vulnerability truly being outstanding is the probability of that, assuming that at least \daMeanOutstandingProbability\ of devices have the fix, i.e. \daMeanOutstandingUncertaintyEquation\ where $n$ is the number of devices contributing to that day's data.
The Python \texttt{uncertainties} library was used to propagate uncertainties through calculations.

@@

\subsubsection{Sensitivity of scoring metric}
\daTabDLDistances
\daTabChangeInScores
To evaluate whether the ranking of different manufacturers is sensitive to the form of the scoring metric we computed the normalised Damerau-Levenshtein distance~\cite{Bard2007} between the lists ordered using different forms of the scoring metric, this is shown in Table~\ref{tab:dl_distances}.
The `equal' metric weights $f$, $u$ and $m$ equally rather than favouring $f$ and makes little difference.
Changing the scoring metric also impacts the scores given for each entity Table~\ref{tab:change_in_scores} shows the mean impact on the scores.
\todo{Give some of the actual orderings as well for the most important ones}
